---
title: "Membership Directory"
toc: true
echo: false
warning: false
---
```{=html}
<style>
.column-screen-inset table.dataTable {
  font-size: 0.75rem;
}
</style>
```
Utilize the table below to find contact information for CCPRO members. The directory is updated quarterly, so please check back for the most current information.

To sign up for the directory, please fill out the [Membership Form](membership-form.qmd) to be added to the list. The directory is updated monthly, so check back for the most recent information. The directory is intended for use by CCPRO members only.

```{r}
#| label: libraries and data
library(dplyr) # Load dplyr for data manipulation
library(stringr) # Load stringr for string manipulation
library(DT) # Load DT for interactive tables
library(readxl) # Load readxl for reading Excel files

directory <- read_excel(
  "../documents/CCPRO_Directory_10312025.xlsx",
  sheet = "CCPRO_Directory"
) |> # Read in the directory from Excel: CCPRO_Directory_10312025.xlsx Sheet: CCPRO_Directory
  mutate(
    college_website = str_remove(college_website, ",$"),
    college_website = ifelse(
      !is.na(college_website) & college_website != "",
      str_glue(
        '<a href="{college_website}" target="_blank">{college_website}</a>'
      ),
      college_website
    ),
    email = ifelse(
      !is.na(email) & email != "",
      str_glue('<a href="mailto:{email}">{email}</a>'),
      email
    )
  ) # Clean up any trailing commas in the college_website column
```

```{r}
#| label: directory table
#| column: screen-inset
directory |>
  select(
    member_name,
    title,
    region,
    college,
    college_website,
    email,
    college_phone,
    college_address,
    sacscoc_liaison,
    executive_committee_member
  ) |>
  datatable(
    escape = FALSE,
    options = list(
      pageLength = 10,
      scrollX = FALSE,
      autoWidth = FALSE,
      dom = "Bfrtip",
      buttons = c("csv", "excel", "pdf")
    ), # Set table length and auto width
    extensions = "Buttons", # Add export buttons
    rownames = FALSE, # Remove row names
    colnames = c(
      "Member Name",
      "Title",
      "Region",
      "College",
      "College Website",
      "Email",
      "Phone",
      "College Address",
      "SACSCOC Liaison",
      "Executive Committee Member"
    ) # Clean column names for display
  )
```
